Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-11 Grassmannian_cells.tex
Some polishing in section 5.1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial description of non-empty cells}\label{sec:combinatorics}
\noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section~\ref{sec:fibrations}.
The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
We give a bijection between these which provides a partial geometric explanation for the combinatorial construction of counting polynomials for rank two quiver Grassmannians given in \cite{rupel}.

@@

  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\to\Gamma(2)$.
  A \emph{2-quiver} is a pair $\cQ=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.  
\end{definition}

The following notion of equivalence for $2$-quivers will be useful in the construction of 2-quivers whose strong successor closed subsets label cells in quiver Grassmannians.
Observe that any quiver can be considered as a 2-quiver with no 2-arrows.
\begin{definition}
  \label{def:2equivalence}
  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\to\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
  \begin{enumerate}
    \item $\Gamma(1)$ has precisely one source $p$; 
    \item $\Gamma(2)$ has precisely one sink $q$;
    \item $\Gamma(1)=\{p\}$ and $\Gamma(2)=\{q\}$.
  \end{enumerate}
  Depending on the condition which is satisfied, we define
  \begin{enumerate}
    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\to\Gamma(2)$;
    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\to \{q\}$;
    \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
  \end{enumerate}
  This defines a relation on the set of $2$-quivers denoted by $\cQ\to\cQ_p$, $\cQ\to\cQ_q$ and $\cQ\to\cQ_V$ respectively.
  Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
\end{definition}

@@

  Let $\beta\subset Q_0$ be strong successor closed in $\cQ$.
  To see that $\beta$ is strong successor closed in $\cQ_p$ it suffices to consider the 2-arrow $V_p:\{p\}\to\Gamma(2)$.
  Suppose $\{p\}\subset\beta$.
  As $\beta$ is successor closed in $Q$ and $p$ is a source in the connected quiver $\Gamma(1)$, we have $\Gamma(1)_0\subset\beta$ and thus $\Gamma(2)_0\cap\beta\ne\varnothing$, i.e.\ $\beta$ is strong successor closed in $\cQ_p$.
  The reverse implication is immediate since $\{p\}\subset\Gamma(1)_0$.

@@

  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\cQ_V$.
  Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\to\{q\}$ for which the claim is obvious as above.
\end{proof}

\begin{remark}
  Below we will usually apply Lemma~\ref{lem:2equivalence} after performing each of the equivalences from Definition~\ref{def:2equivalence}.
  That is, given a 2-arrow $V:\Gamma(1)\to\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
\end{remark}

@@

\begin{remark}
  \label{rem:2-arrows Q2}
  The 2-arrows of $\cQ_2$ should be viewed as a reflection of the isomorphism
  \begin{equation}
    \label{eq:case2}
    \Ext(P_2,P_1)
    \cong\bigoplus_{i=1}^n \Ext(\tilde P_2,\tilde P_{1,i})
    \cong\big\langle (2,e)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
  \end{equation}
  and the inclusions of $\cQ_2^{[t]}$ in $\cQ_2^{[r]}$ for $t\ge r$ as a reflection of the surjections $\Ext(P_2^{[t]},P_1)\onto\Ext(P_2^{[r]},P_1)$.
  In particular, the isomorphism \eqref{eq:case2} can be used with these surjections to obtain compatible bases for each $\Ext(P_2^{[r]},P_1)$.
\end{remark}
The $2$-quiver $\mathcal Q_2^{[r]}$ given above is clearly equivalent to the support quiver \eqref{coeff} thought of as a 2-quiver with no 2-arrows:
\begin{align}
  \label{coeff}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r})}
\end{align}
In this way we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.
In this way we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.

The 2-quiver $\cQ_3^{[r]}$ associated to $\tilde P_3^{[r]}$ has underlying quiver $Q_3^{[r]}:=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{2,i}$.
Note that we are not taking this union as subquivers of $\widetilde{K(n)}$, in particular each quiver $Q_{2,i}$ has a vertex which can be associated to $(1,e)$ in $\widetilde{K(n)}$ but these are not identified in the quiver $Q_3^{[r]}$. 
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
By Lemma~\ref{lem:2equivalence}, we obtain an equivalent 2-quiver by replacing each $\Gamma_s(2)$ above with the corresponding sink $(1,e)$ taken as a vertex of $Q_{2,s}$.
By a slight abuse of notation, below we will let $\cQ_3^{[r]}$ denote this equivalent 2-quiver.
Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
\[
\begin{tikzpicture}[scale=1.35]
  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

We are now ready to define the 2-quivers $\cQ_{m+1}^{[r]}$ for $m\ge3$.
This will be by induction, so assume we have already constructed the 2-quivers $\cQ_m^{[s]}$ for $0\le s\le n-1$ and define the 2-quivers $\cQ_{m,i}^{[s]}:=\alpha_i^{(-1)^{m+1}}.\cQ_m^{[s]}$ for $1\le i\le n$. 
Then we may take the underlying quiver of $\cQ_{m+1}^{[r]}$ to be
\begin{equation}
  \label{eq:recursive 2-quivers}
  Q_{m+1}^{[r]}:=
  \begin{cases}
    Q_{m,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{m,i} & \text{if $m$ is even;}\\
    Q_{m,1}^{[1]}\sqcup\coprod\limits_{i=2}^{n-r} Q_{m,i} & \text{if $m$ is odd.}
  \end{cases}
\end{equation}
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
\begin{remark}
  For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[s]}\cong\tilde P_{m-1}^{[s]}$ can uniquely be found as a quotient of $\tilde P_{m,s}$.
  This is reflected in the structure of the $2$-quivers as we can find $\cQ_{m-1}^{[s]}$ as a subquiver of $\cQ_{m,s}$.
  In the diagrams for 2-quivers given here, this sub-2-quiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,s}$.
\end{remark}

\begin{flushleft}
\begin{tikzpicture}[scale=0.97]
\draw (0,4) node (A1) {\footnotesize$Q_{m-1,1}$}
  +(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,r}$}
  +(1.65,0) node (B1) {\footnotesize$Q_{m-1,2}$}
  +(1.65,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$}
  +(3,0) node (B11) {\footnotesize$\dots$}
  +(4.55,0) node (D1) {\footnotesize$Q_{m-1,n-1}$}
  +(4.55,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}
  +(6.4,0) node (E1) {\footnotesize$Q_{m-2,2}$}
  +(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}
  +(7.75,0) node (A1b) {\footnotesize$\dots$}
  +(9.6,0) node (B1b) {\footnotesize$Q_{m-2,r+1}$}
  +(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[r]}$}
  +(11.2,0) node (B11b) {\footnotesize$\dots$}
  +(12.8,0) node (D1b) {\footnotesize$Q_{m-2,n-1}$}
  +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$}
  +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$};
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[implies-,double equal sign distance,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q81)--(A1) node[pos=.5,above] {};

\draw (4.45,0) node (B) {$\mathcal Q_{m,r+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[r]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

@@

\node (PMK) [draw=black,fit={(Q2b) (B)}]{};
\draw[-implies,double equal sign distance,red,thick] (PMK)--(P11b);
\end{tikzpicture}
\\
\end{flushleft}
\noindent 
As already mentioned two different vertices of $\mathcal Q_m^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe(\beta)$ and  $\bfe(\beta)$ of a subset $\beta\subset(\mathcal Q_m^{[r]})_0$ are defined by
\[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in\beta\subset(\mathcal Q_m^{[r]})_0$.

\begin{theorem}\mbox{}
  \label{thm:2quivercells}
  \begin{enumerate}
    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_m^{[r]}\big)$ (resp. $Gr_\bfe\big(P_m^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\mathcal Q_m^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp. $\bfe\in\NN^{K(n)_0}$) yielding a one-to-one correspondence between cells and strong successor closed subsets.
    \item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp. $\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[r]}))$ (resp. $\chi(\Gr_{\bfe }(P_m^{[r]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$ (resp. $\bfe$) of the $2$-quiver of $\mathcal Q_m^{[r]}$.
  \end{enumerate}
\end{theorem}
\begin{proof}
The results of Sections~\ref{sec:bb} and \ref{torusaction} imply that the statements in parentheses follow from the respective results for the lifted representations. Moreover, the second result follows from the first one.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial description of non-empty cells}
\label{sec:combinatorics}
\noindent In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition in Section~\ref{sec:fibrations}.
The second is the notion of compatible pairs in a maximal Dyck path arising in the computation of rank 2 cluster variables \cite{llz}.
We give a bijection between these which provides a partial geometric explanation for the combinatorial construction of counting polynomials for rank two quiver Grassmannians given in \cite{rupel}.

@@

  A \emph{2-arrow} of the quiver $Q$ is an ordered pair $V=\big(\Gamma(1),\Gamma(2)\big)$ of full connected subquivers of $Q$, these will be denoted $V:\Gamma(1)\implies\Gamma(2)$.
  A \emph{2-quiver} is a pair $\cQ=(Q,Q_2)$ consisting of a quiver $Q$ and a collection $Q_2$ of 2-arrows of $Q$.
  Given a 2-quiver $\cQ$, we call a subset $\beta\subset Q_0$ \emph{strong successor closed in $\cQ$} if it is successor closed in $Q$ and for each 2-arrow $V:\Gamma(1)\implies\Gamma(2)$ in $Q_2$ with $\Gamma(1)_0\subset\beta$ we have $\Gamma(2)_0\cap\beta\ne\varnothing$.  
\end{definition}

The following notion of equivalence for $2$-quivers will be useful in the construction of 2-quivers whose strong successor closed subsets label cells in quiver Grassmannians.
Observe that any quiver can be considered as a 2-quiver with no 2-arrows.
\begin{definition}
  \label{def:2equivalence}
  Let $\cQ=(Q,Q_2)$ be a $2$-quiver with a $2$-arrow $V:\Gamma(1)\implies\Gamma(2)$ in $Q_2$ such that one of the following conditions is satisfied:
  \begin{enumerate}
    \item $\Gamma(1)$ has precisely one source $p$; 
    \item $\Gamma(2)$ has precisely one sink $q$;
    \item $\Gamma(1)=\{p\}$ and $\Gamma(2)=\{q\}$.
  \end{enumerate}
  Depending on the condition which is satisfied, we define
  \begin{enumerate}
    \item $\cQ_p$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_p:\{p\}\implies\Gamma(2)$;
    \item $\cQ_q$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a $2$-arrow $V_q:\Gamma(1)\implies\{q\}$;
    \item $\cQ_V$ as the $2$-quiver obtained from $\cQ$ when replacing the $2$-arrow $V$ by a usual arrow $\alpha_V:p\to q$. 
  \end{enumerate}
  This defines a relation on the set of $2$-quivers denoted by $\cQ\to\cQ_p$, $\cQ\to\cQ_q$ and $\cQ\to\cQ_V$ respectively.
  Moreover, it induces an equivalence relation $\sim$ on the set of $2$-quivers when taking the symmetric and transitive closure of this relation. 
\end{definition}

@@

  Let $\beta\subset Q_0$ be strong successor closed in $\cQ$.
  To see that $\beta$ is strong successor closed in $\cQ_p$ it suffices to consider the 2-arrow $V_p:\{p\}\implies\Gamma(2)$.
  Suppose $\{p\}\subset\beta$.
  As $\beta$ is successor closed in $Q$ and $p$ is a source in the connected quiver $\Gamma(1)$, we have $\Gamma(1)_0\subset\beta$ and thus $\Gamma(2)_0\cap\beta\ne\varnothing$, i.e.\ $\beta$ is strong successor closed in $\cQ_p$.
  The reverse implication is immediate since $\{p\}\subset\Gamma(1)_0$.

@@

  Finally, let $\beta\subset(Q_V)_0$ be strong sucessor closed in $\cQ_V$.
  Since $Q_1\subset(Q_V)_1$, we immediately see that $\beta$ is successor closed in $Q$.
  To see that $\beta$ is strong successor closed in $\cQ$, it suffices to consider the 2-arrow $V:\{p\}\implies\{q\}$ for which the claim is obvious as above.
\end{proof}

\begin{remark}
  Below we will usually apply Lemma~\ref{lem:2equivalence} after performing each of the equivalences from Definition~\ref{def:2equivalence}.
  That is, given a 2-arrow $V:\Gamma(1)\implies\Gamma(2)$ for which $\Gamma(1)$ has a unique source $p$ and $\Gamma(2)$ has a unique sink $q$, we get an equivalent 2-quiver by replacing this 2-arrow with a usual arrow $a_V:p\to q$.
\end{remark}

@@

\begin{remark}
  \label{rem:2-arrows Q2}
  The 2-arrows of $\cQ_2$ should be viewed as a reflection of the isomorphism
  \begin{equation}
    \label{eq:case2}
    \Ext(P_2,P_1)
    \cong\bigoplus_{i=1}^n \Ext(\tilde P_2,\tilde P_{1,i})
    \cong\big\langle (2,e)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
  \end{equation}
  and the inclusions of $\cQ_2^{[t]}$ in $\cQ_2^{[r]}$ for $t\ge r$ as a reflection of the surjections $\Ext(P_2^{[t]},P_1)\onto\Ext(P_2^{[r]},P_1)$.
  In particular, the isomorphism \eqref{eq:case2} can be used with these surjections to obtain compatible bases for each $\Ext(P_2^{[r]},P_1)$.
\end{remark}
The $2$-quiver $\mathcal Q_2^{[r]}$ given above is clearly equivalent to the support quiver \eqref{coeff} thought of as a 2-quiver with no 2-arrows:
\begin{align}
  \label{coeff}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r}).}
\end{align}
Thus we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.
In this way, we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.

The 2-quiver $\cQ_3^{[r]}$ associated to $\tilde P_3^{[r]}$ has underlying quiver $Q_3^{[r]}:=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{2,i}$.
Note that we are not taking this union as subquivers of $\widetilde{K(n)}$, in particular each quiver $Q_{2,i}$ has a vertex which can be associated to $(1,e)$ in $\widetilde{K(n)}$ but these are not identified in the quiver $Q_3^{[r]}$. 
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\implies\Gamma_s(2)$ of $\cQ_3^{[r]}$ given by $\Gamma_s(1)=Q_{2,n}^{[1]}\sqcup\coprod\limits_{i=s+1}^{n-1} Q_{2,i}$ with $\Gamma_s(2)\subset Q_{2,s}$ the subquiver $(2,\alpha_s^{-1})\xrightarrow{\alpha_s} (1,e)$.
By Lemma~\ref{lem:2equivalence}, we obtain an equivalent 2-quiver by replacing each $\Gamma_s(2)$ above with the corresponding sink $(1,e)$ taken as a vertex of $Q_{2,s}$.
By a slight abuse of notation, below we will let $\cQ_3^{[r]}$ denote this equivalent 2-quiver.
Then $\cQ_3^{[r]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
\[
\begin{tikzpicture}[scale=1.35]
  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} +(0.1,-1.3) node {\footnotesize$\mathcal Q_3$}; 
  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

@@

We are now ready to define the 2-quivers $\cQ_{m+1}^{[r]}$ for $m\ge3$.
This will be by induction, so assume we have already constructed the 2-quivers $\cQ_m^{[s]}$ for $0\le s\le n-1$ and define the 2-quivers $\cQ_{m,i}^{[s]}:=\alpha_i^{(-1)^{m+1}}.\cQ_m^{[s]}$ for $1\le i\le n$. 
Then we may take the underlying quiver of $\cQ_{m+1}^{[r]}$ to be
\begin{equation}
  \label{eq:recursive 2-quivers}
  Q_{m+1}^{[r]}:=
  \begin{cases}
    Q_{m,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{m,i} & \text{if $m$ is even;}\\
    Q_{m,1}^{[1]}\sqcup\coprod\limits_{i=2}^{n-r} Q_{m,i} & \text{if $m$ is odd.}
  \end{cases}
\end{equation}
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\implies\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
\begin{remark}
  For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[s]}\cong\tilde P_{m-1}^{[s]}$ can uniquely be found as a quotient of $\tilde P_{m,s}$.
  This is reflected in the structure of the $2$-quivers as we can find $\cQ_{m-1}^{[s]}$ as a subquiver of $\cQ_{m,s}$.
  In the diagrams for 2-quivers given here, this sub-2-quiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,s}$.
\end{remark}

\[
\begin{tikzpicture}[scale=0.97]
\draw (0,4) node (A1) {\footnotesize$Q_{m-1,1}$}
  +(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,r}$}
  +(0,-4.2) node {$\cQ_{m+1}^{[r-1]}$}
  +(1.65,0) node (B1) {\footnotesize$Q_{m-1,2}$}
  +(1.65,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$}
  +(3,0) node (B11) {\footnotesize$\dots$}
  +(4.55,0) node (D1) {\footnotesize$Q_{m-1,n-1}$}
  +(4.55,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}
  +(6.4,0) node (E1) {\footnotesize$Q_{m-2,2}$}
  +(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}
  +(7.75,0) node (A1b) {\footnotesize$\dots$}
  +(9.6,0) node (B1b) {\footnotesize$Q_{m-2,r+1}$}
  +(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[r]}$}
  +(11.125,0) node (B11b) {\footnotesize$\dots$}
  +(12.7,0) node (D1b) {\footnotesize$Q_{m-2,n-1}$}
  +(12.7,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$}
  +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$};
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[implies-,double equal sign distance,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q81)--(A1) node[pos=.5,above] {};

\draw (4.45,0) node (B) {\footnotesize$Q_{m,r+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[r]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {\footnotesize$Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0.25) node (D) {\footnotesize$Q_{m,n-1}$}  +(10,0.25) node (E) {\footnotesize$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.35) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

@@

\node (PMK) [draw=black,fit={(Q2b) (B)}]{};
\draw[-implies,double equal sign distance,red,thick] (PMK)--(P11b);
\end{tikzpicture}
\]
As already mentioned two different vertices of $\mathcal Q_{m+1}^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe(\beta)$ and  $\bfe(\beta)$ of a subset $\beta\subset(\mathcal Q_{m+1}^{[r]})_0$ are defined by
\[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}}\qquad\text{and}\qquad\bfe(\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in\beta\subset(\mathcal Q_{m+1}^{[r]})_0$.
\begin{theorem}\mbox{}
  \label{thm:2quivercells}
  \begin{enumerate}
    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_{m+1}^{[r]}\big)$ (resp. $\Gr_\bfe\big(P_{m+1}^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\cQ_{m+1}^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp. $\bfe\in\NN^{K(n)_0}$) yielding a one-to-one correspondence between cells and strong successor closed subsets.
    \item For $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp. $\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_\tbfe(\tilde P_{m+1}^{[r]}))$ (resp. $\chi(\Gr_{\bfe }(P_{m+1}^{[r]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$ (resp. $\bfe$) of the $2$-quiver of $\cQ_{m+1}^{[r]}$.
  \end{enumerate}
\end{theorem}
\begin{proof}
  The results of Sections~\ref{sec:bb} and \ref{torusaction} imply that the statements in parentheses follow from the respective results for the lifted representations.
  Moreover, the second result follows from the first one.
